Gaussian mean estimation in simulated data sets

### 2018-12-10 analysis/gaussmeanest.Rmd
Added pointers to dsc/README in relevant R Markdown files.

Since the simulation experiments are computationally intensive, they
were implemented separately (see the "dsc" directory in this git
repository), and here we only create plots to summarize the results of
these experiments.

>>>>

Since the simulation experiments are computationally intensive, they
were implemented separately. (For instructions on re-running these
simulation experiments, see the README in the "dsc" directory of the
git repository). Here we create plots to summarize the results of
these experiments.
